---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ansperf

<!-- badges: start -->
<!-- badges: end -->

Workspace for the development of a GANP/PBWG/BRA-EUR/CHN-EUR informed package.

The general objective of air navigation services is to enable the "... safe, efficient, and orderly flow of air traffic."
ICAO promotes further the use of a performance-based approach and encourages stakeholder to monitor and benchmark services.
For this purpose a set of (global) key performance indicators (KPI) were established under the Global Air Navigation Plan. 
These KPIs (and variants of them) are actively used by the performance benchmarking community.

This package is jointly developed by the Department of Airspace Control (DECEA) und EUROCONTROL.
Performance groups of both organisations are committed to further harmonise the use of the KPIs as part of the bi-lateral and multi-lateral/international work.

The `{ansperf}` package implements the common KPIs and supporting metrics in `R`.

The project is in its active development phase and may change frequently.   
Do not hesitate to reach out, if you have an interest in contributing, testing, or have any other question about the on-going developments.


## Installation

You can install the development version of ansperf from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("euctrl-pru/ansperf")
```

## GANP KPIs

The `performance framework` of the GANP lists the following KPIs (c.f. https://www4.icao.int/ganpportal/ASBU/KPI) and whether `{ansperf}` has it implemented:

```{r}
load("./data/data_ganp_kpi_reqs.rda")

#gt::gt(data_ganp_kpi_reqs) |> 
#  gt::sub_missing(missing_text = "")
tinytable::tt(data_ganp_kpi_reqs)
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ansperf)
## basic example code
```

The examples/getting started vignette will be built soon.
