---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Operational ANS Performance with R

<!-- badges: start -->
<!-- badges: end -->

The goal of `{ansperf}` is to provide a enable interested stakeholders to undertake a standardised operational performance analysis in accordance with the ICAO Global Air Navigation Plan and/or variants used by the international performance benchmarking community.

The package is based on the work of the Performance Section of DECEA Brazil and the Performance Review Unit of EUROCONTROL. 

This is an initial setup. Thus, the content is heavily under development.
Please come back for any updates.

## Installation

You can install the development version of the `{ansperf}` package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("euctrl-pru/ansperf")
```

## Ways of Working

### Development Roadmap

During the project meeting 28. June, it was agreed to proceed as follows:

1. implement the ICAO GANP KPI catalogue (step-by-step) with a focus on the BRA-EUR indicators
1. augment KPIs with PBWG variants (as far as practicable)
1. advance state-of-the-art by adding new (and advanced) methods, e.g. trajectory processing
1. any future development idea

### Reduce Overhead - Fail Early

We try to organise the development through issues (in github).
For each issue, we branch!
When merging, cross-reference issue.

## How to Use This Package

This is a placeholder. It will go into other vignettes at a later point in time.

```{r example}
library(ansperf)
## basic example code
```


## How to Update the README

We work with `README.Rmd` instead of just `README.md`.
This allows to include R chunks like the following:

```{r cars}
summary(cars)
```

But it requires to still need to render `README.Rmd` regularly with a view to keep `README.md` up-to-date. 
`devtools::build_readme()` is handy for this.
Run this, to update the README.Rmd --> README.md. Then push!

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
